### 2019-07-30 thesis.tex
* thesis.tex: Summary: another day writing the thesis...

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, and scale lengths\footnote{For a relatively brief, but
  comprehensive, description of the scales and characteristics of cosmic plasmas,
  see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state\cite{may}. Most of these plasmas are quite
far from our measurement instruments, being accessible only through analysis of
the electromagnetic spectrum emitted from their remote location.

>>>>

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
  brief, but comprehensive, description of the scales and characteristics of
  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter in the universe is in the plasma state\cite{may}. Under
cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
around galaxies or in the atmosphere of cold stars have a strong reaction to
electromagnetic fields, exhibiting the characteristic collective behavior of
plasmas\cite{tsypa,peratt2014}.
Since this ubiquity of plasmas in space came as a fact, astrophysicists and
plasma physicists have been increasingly exchanging knowledge, with plasma
physics providing theoretical background and laboratory models that might help
with the interpretation and physical explanation of astrophysical observations,
and astrophysics confirming theoretical predictions of plasma physics with
observations of phenomena that are unique to space plasma\cite{tsypa,Kulsrud2005}.

The absolute majority of the plasma observed in space is far away from us,
being accessible only through analysis of the electromagnetic spectrum
emitted from their quite remote location. A fortunate exception to this
fact is the plasma in our solar system.
